---
title: "Course 9 - Developing Data Products - Week 4 Assignment 3 Pitch"
author: "Leona288"
date: "14 August 2018"
output:
  ioslides_presentation:
    fig_caption: yes
    fig_height: 3
    fig_retina: 1
    fig_width: 5
    smaller: yes
  slidy_presentation: default
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Reproducible Pitch Presentation Requirements

- 5 slides (inclusive of the title slide) to pitch about the app. 
- Create a web page using Slidify or Rstudio Presenter with an html5 slide deck.
- Your presentation pushed to github or Rpubs
- A link to your github or Rpubs presentation pasted into the provided text box

## Introduction

The data for the app is based on the mtcars data in R.
The model provides the user with an interface to predict the miles per gallon based on the input on the weight of the car.

How to use the app

1. Select the weight of the car through moving the slider.
2. Hit the "Submit" button after selection.
3. The estimated miles per gallon based on the model is given in the text below the chart.
4. There is an option to deselect the regression line.

## The codes for the output to shiny are as follows:
- ui.R (for user interface) that controls how it looks and
- server.R that controls what it does.

The link to the app is:
https://github.com/leona288/Course-9---Developing-Data-Products

##

```{r, echo=FALSE}
library(shiny)
shinyUI(fluidPage(
        titlePanel("Predict MPG from Weight"),
        sidebarLayout(
                sidebarPanel(
                        sliderInput("sliderwt", "What is the weight of the car?", 1, 6, value = 3),
                        checkboxInput("showModel1", "Show/Hide Model", value = TRUE),
                        submitButton("Submit")
                ),
                mainPanel(
                        plotOutput("plot1"),
                        h6("Predicted MPG from Model:"),
                        textOutput("pred1")
                )
        )
))
```


```{r, echo=FALSE}
library(shiny)
shinyServer(function(input, output) {
        mtcars$wtsp <- ifelse(mtcars$wt - 3 > 0, mtcars$mpg - 3, 0)
        model1 <- lm(mpg ~ wt, data = mtcars)
        
        model1pred <- reactive({
                wtInput <- input$sliderwt
                predict(model1, newdata = data.frame(wt = wtInput))
        })
        
        output$plot1 <- renderPlot({
                wtInput <- input$sliderwt
                
                plot(mtcars$wt, mtcars$mpg, xlab = "Weight", 
                     ylab = "Miles per Gallon", bty = "n", pch = 16,
                     xlim = c(1, 6), ylim = c(10, 35))
                if(input$showModel1){
                        abline(model1, col = "red", lwd = 2)
                }
                legend(25, 250, "Model 1 Prediction", pch = 16, 
                       col = "red", bty = "n", cex = 1.2)
                points(wtInput, model1pred(), col = "red", pch = 16, cex = 2)
        }, height = 200, width = 300)
        
        output$pred1 <- renderText({
                model1pred()
        })
})



```




